Offline Mode for Corporate Mobile Client Security Architecture

### 2016-06-18 docs/papers/2016JGC/2016JGC.tex
table fix

@@

@@

\begin{table}
	\caption{Speed of decryption on a client device}
	\label{tab:01}
	\centering
	\begin{tabular}{l|l|l|l|l|l}
		Device Model	& File set size	& Mean time of getting decrypted stream (ABE)	& Mean time of decrypting content (AES)	& Mean time of copying file without decrypt	& Mean time of decryption (the whole file)  \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		Samsung SM-T320 Galaxy Tab Pro 8.4	& 10 mb	& 1041 ms	& 4230 ms	& 298 ms		& 5271 ms	\\
		Samsung SM-T320 Galaxy Tab Pro 8.4	& 1 mb	& 811 ms		& 319 ms		& 23 ms		& 1130 ms	\\
		Samsung SM-T320 Galaxy Tab Pro 8.4	& 1 kb	& 1078 ms	& 1 ms		& 0 ms		& 1080 ms	\\
		Samsung GT-I9190 Galaxy S4 Mini		& 1 b	& 1167ms		& 2 ms		& 0 ms		& 1169 ms	\\
		Samsung GT-I9190 Galaxy S4 Mini		& 1 kb	& 1141ms		& 2 ms		& 0 ms		& 1144 ms	\\
		Samsung GT-I9190 Galaxy S4 Mini		& 1 mb	& 1138 ms	& 368 ms		& 35 ms		& 1506 ms	\\
		Samsung GT-I9190 Galaxy S4 Mini		& 10 mb	& 1131 ms	& 3618 ms	& 324 ms		& 4750 ms	\\
		\noalign{\smallskip}\hline
	\end{tabular}
\end{table}

@@

\begin{table}
	\caption{Speed of receiving the list of files}
	\label{tab:02}
	\centering
	\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
		Files quantity 	& \# Samples 	& Average (ms) 	& Min (ms) 	& Max (ms) 	& Std. Dev. 	& Error (\%)		& Throughput 	& KB/sec 	& Avg. Bytes \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		1		& 1000	& 131	& 29		& 321	& 31.56		& 0.00\%		& 74		& 161.32		& 2233	\\
		10		& 1000	& 154	& 37		& 269	& 32.24		& 0.00\%		& 63.4	& 659.79		& 10656	\\
		100		& 1000	& 396	& 68	 	& 1055	& 87.56		& 0.00\%		& 25		& 2323.2		& 95308	\\
		1000		& 1000	& 2879	& 475	& 4634	& 496.02		& 0.00\%		& 3.4	& 3178		& 946311	\\
		\noalign{\smallskip}\hline
	\end{tabular}
\end{table}

@@

\begin{table}
	\caption{Speed of generating the user keys}
	\label{tab:03}
	\centering
	\begin{tabular}{l|l|l|l|l|l|l|l|l}
		Label	& \# Samples	& Average (ms)	& Min (ms)	& Max (ms)	& Std. Dev.	& Throughput		& KB/sec		& Avg. Bytes \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		Login 5 shares available		& 1000	& 982	& 225	& 1990	& 271.88		& 20.1	& 146.36		& 7459	\\
		Login 10 shares available	& 1000	& 1140	& 340	& 4176	& 459.3		& 17.3	& 223.88		& 13218	\\
		Login 25 shares available	& 1000	& 1267	& 887	& 2303	& 192.75		& 15.5	& 294.55		& 19466 \\
		\noalign{\smallskip}\hline
	\end{tabular}
\end{table}

>>>>

% table
\usepackage{color, colortbl}
\definecolor{Gray}{gray}{0.9}

@@

\begin{table*}[!t]
	\caption{Speed of decryption on a client device}
	\label{tab:01}
	\centering
	\begin{tabular}{|l|l|l|l|l|l|}
		\hline \rowcolor{Gray} Device Model	& File set size	& \begin{tabular}[x]{@{}l@{}}Mean time of\\getting decrypted\\stream (ABE)\end{tabular}	& \begin{tabular}[x]{@{}l@{}}Mean time of\\decrypting \\content (AES)\end{tabular}	& \begin{tabular}[x]{@{}l@{}}Mean time of\\copying file\\without decrypt\end{tabular}	& \begin{tabular}[x]{@{}l@{}}Mean time of\\decryption\\(the whole file)\end{tabular}	\\ \hline

		\begin{tabular}[x]{@{}l@{}}Samsung SM-T320 Galaxy\\Tab Pro 8.4\end{tabular}	& 10 mb	& 1041 ms	& 4230 ms	& 298 ms		& 5271 ms	\\ \hline
		\begin{tabular}[x]{@{}l@{}}Samsung SM-T320 Galaxy\\Tab Pro 8.4\end{tabular}	& 1 mb	& 811 ms		& 319 ms		& 23 ms		& 1130 ms	\\ \hline
		\begin{tabular}[x]{@{}l@{}}Samsung SM-T320 Galaxy\\Tab Pro 8.4\end{tabular}	& 1 kb	& 1078 ms	& 1 ms		& 0 ms		& 1080 ms	\\ \hline
		\begin{tabular}[x]{@{}l@{}}Samsung GT-I9190 Galaxy\\S4 Mini\end{tabular}		& 1 b	& 1167ms		& 2 ms		& 0 ms		& 1169 ms	\\ \hline
		\begin{tabular}[x]{@{}l@{}}Samsung GT-I9190 Galaxy\\S4 Mini\end{tabular}		& 1 kb	& 1141ms		& 2 ms		& 0 ms		& 1144 ms	\\ \hline
		\begin{tabular}[x]{@{}l@{}}Samsung GT-I9190 Galaxy\\S4 Mini\end{tabular}		& 1 mb	& 1138 ms	& 368 ms		& 35 ms		& 1506 ms	\\ \hline
		\begin{tabular}[x]{@{}l@{}}Samsung GT-I9190 Galaxy\\S4 Mini\end{tabular}		& 10 mb	& 1131 ms	& 3618 ms	& 324 ms		& 4750 ms	\\ \hline
	\end{tabular}
\end{table*}

@@

\begin{table*}[!t]
	\caption{Speed of receiving the list of files}
	\label{tab:02}
	\centering
	\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
		\hline \rowcolor{Gray} \begin{tabular}[x]{@{}l@{}}Files\\quantity\end{tabular}	 	& Samples 	& \begin{tabular}[x]{@{}l@{}}Average\\(ms)\end{tabular}	 	& Min (ms) 	& Max (ms) 	& Std. Dev. 	& Error (\%)		& Throughput 	& KB/sec 	& Avg. Bytes \\ \hline
		1		& 1000	& 131	& 29		& 321	& 31.56		& 0.00\%		& 74		& 161.32		& 2233	\\ \hline		
		10		& 1000	& 154	& 37		& 269	& 32.24		& 0.00\%		& 63.4	& 659.79		& 10656	\\ \hline
		100		& 1000	& 396	& 68	 	& 1055	& 87.56		& 0.00\%		& 25		& 2323.2		& 95308	\\ \hline
		1000		& 1000	& 2879	& 475	& 4634	& 496.02		& 0.00\%		& 3.4	& 3178		& 946311	\\ \hline
	\end{tabular}
\end{table*}

\begin{table*}
	\caption{Speed of generating the user keys}
	\label{tab:03}
	\centering
	\begin{tabular}{|l|l|l|l|l|l|l|l|l|}
		\hline \rowcolor{Gray} Label	& Samples	& \begin{tabular}[x]{@{}l@{}}Average\\(ms)\end{tabular}	& Min (ms)	& Max (ms)	& Std. Dev.	& Throughput		& KB/sec		& Avg. Bytes \\ \hline
		\begin{tabular}[x]{@{}l@{}}Login 5\\shares\\available\end{tabular}		& 1000	& 982	& 225	& 1990	& 271.88		& 20.1	& 146.36		& 7459	\\ \hline
		\begin{tabular}[x]{@{}l@{}}Login 10\\shares\\available\end{tabular}	& 1000	& 1140	& 340	& 4176	& 459.3		& 17.3	& 223.88		& 13218	\\ \hline
		\begin{tabular}[x]{@{}l@{}}Login 25\\shares\\available\end{tabular}	& 1000	& 1267	& 887	& 2303	& 192.75		& 15.5	& 294.55		& 19466 \\ \hline
	\end{tabular}
\end{table*}

@@

@@
